---
title: "LCZ Preprocessing"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(randomForest)
library(raster)
library(rgdal)
library(here)
library(mapproj)
```

The LCZ data does not come with a polygon id it has to be added. This requires some work in QGIS before bringing the dtat into R, rasterizing, and saving as a dataframe in `results/lcz_and_poly_ids.rds` Here is the process:

### 1. Steps in QGIS

1. raster to vector
2. dissolve by attribute
3. multipart to singlepart
4. field calculator to make row number (and therefore polygon #) an attribute

### 2. Steps in R                                 

Read in file from QGIS

```{r}
singleparts <- readOGR(here("data/hong_kong/lcz_polyid_shapefile", "singleparts.shp"))
```

Read in original LCZ raster file to have information on the extent

```{r}
train <- brick(here("data/hong_kong/lcz/", "hong_kong_lcz_gt.tif"))
```

Rasterize the shapefile from QGIS using the extent of the original raster file. 

```{r}
rasterized_singleparts <- rasterize(singleparts, train)
```

Transform to dataframe

```{r}
rsp_df <- as.data.frame(rasterized_singleparts)
```

Save

```{r}
saveRDS(rsp_df, here("results", "lcz_and_poly_ids.RDS"))
```

