---
title: "Getting the Landsat Data into R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

libraries 

```{r}
library(randomForest)
library(raster)
library(rgdal)
library(here)
#training <- readOGR('training_data.shp', layer='training_data')
train <- brick(here("../train/hong_kong/lcz/", "hong_kong_lcz_col.tif"))
#le7 <- brick('LE70220491999322EDC01_stack.gtif')
le8 <- brick(here("../train/hong_kong/landsat_8", "LC81220442015291LGN00/LC81220442015291LGN00_B1.tif"))
```


Definitely didn't work and was just for testing (to see if I could go through the tutorial code with my data) anyway, so scrap it.

Tomorrow:
1. Why did they give us the data as a tif instead of a shp file? Is that advantageous?
2. If it's not, how do I convert it to a point shapefile?
3. Watch WUDAPT video

what is saga? - alternative to arc or qgis

*Updated filepaths, watched WUDAPT, trying stacking them into a RasterStack*

```{r}
all_data <- stack(le8, train)
all_data_added <- addLayer(train, le8)
```

Now what exactly is a RasterStack? 

```{r}
summary(all_data)
```
